DESING AND SIMULATION SOFTWARE FOR RHODOTRON TYPE ELECTRON ACCELERATORS

### 2023-08-17 subsections/design/cavity/cavity.tex
changes from Erkcan & Gokhan hocas

In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
    \begin{aligned}
        f_{107.5} = 107.5 \textrm{ MHz} \\
        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
        R_1 = \frac{R_2}{4} = 0.188 m \\
        h = \frac{\lambda}{2} = 1.394 m 
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        f_{180} = 180 \textrm{ MHz} \\
        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
        R_1 = \frac{R_2}{4} = 0.113 m \\
        h = \frac{\lambda}{2} = 0.833 m 
    \end{aligned}
\end{eqnarray}
In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish107.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:107_simple_cavity_design}
\end{figure}

>>>>

In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and it will be the focus of all further calculations.
Using $f_{RF}=107.5$ MHz \& $f_{RF}=180$ MHz for comparison:
\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
    \begin{aligned}
        f_{107.5} = 107.5 \textrm{ MHz} \\
        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
        R_1 = \frac{R_2}{4} = 0.188 m \\
        h = \frac{\lambda}{2} = 1.394 m 
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        f_{180} = 180 \textrm{ MHz} \\
        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
        R_1 = \frac{R_2}{4} = 0.113 m \\
        h = \frac{\lambda}{2} = 0.833 m 
    \end{aligned}
\end{eqnarray}
In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish107.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:107_simple_cavity_design}
\end{figure}

### 2023-08-17 subsections/design/first_design/first_design.tex
changes from Erkcan & Gokhan hocas

A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.5\linewidth]{../../../figures/cst/cst_first_design1.png}
    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
    \label{fig:initial_design}
\end{figure}
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_design3.png}
      \caption{Axial cross section.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_design2.png}
      \caption{Cross section at acceleration plane.}
    \end{subfigure}
    \caption{Initial design of the proposed rhodotron.}
    \label{fig:initial_design_cross_section}
\end{figure}
The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_magnet_design1.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_magnet_design2.png}
    \end{subfigure}
    \caption{Initial magnet design.}
    \label{fig:initial_magnet_design}
\end{figure}

@@

In KAHVELab, several improvements were made to these initial designs together with \textit{Mr. Sinan ÖZ}. They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
Improved designs can be seen in the figures below.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_sinan_cavity_design1.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.94\linewidth]{../../../figures/cst/cst_sinan_cavity_design2.png}
    \end{subfigure}
    \caption{Improved cavity design.}
    \label{fig:improved_cavity_design}
\end{figure}

>>>>

A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
Frequency was selected to benefit from the RF power supply units at hand.
After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.5\linewidth]{../../../figures/cst/cst_first_design1.png}
    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
    \label{fig:initial_design}
\end{figure}
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_design3.png}
      \caption{Axial cross section.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_design2.png}
      \caption{Cross section at acceleration plane.}
    \end{subfigure}
    \caption{Initial design of the proposed rhodotron.}
    \label{fig:initial_design_cross_section}
\end{figure}
The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_magnet_design1.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_magnet_design2.png}
    \end{subfigure}
    \caption{Initial magnet design.}
    \label{fig:initial_magnet_design}
\end{figure}

@@

Several improvements were made to KAHVELab Rhodotron initial designs \cite{sinan}. These include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
Improved designs can be seen in the figures below.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_sinan_cavity_design1.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.94\linewidth]{../../../figures/cst/cst_sinan_cavity_design2.png}
    \end{subfigure}
    \caption{Improved cavity design.}
    \label{fig:improved_cavity_design}
\end{figure}

### 2023-08-17 subsections/design/magnet/magnet.tex
changes from Erkcan & Gokhan hocas

\section{Magnet Design} \label{sec:magnet_design}
Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/Ltot.png}
      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/tt300_mag.png}
      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
    \end{subfigure}
    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
    \label{fig:magnet_design_illustrations}
\end{figure}
In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.

@@

To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field. 
In other words, total trajectory of synchronous particle needs to satisfy the following equality;
\begin{equation*}
    L_{pass} = n \lambda
\end{equation*} 
Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
\begin{equation}
    L_{pass} = \lambda
\end{equation}

\begin{figure}[H]    
    \centering
    \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
    \caption{Trejectory of a particle in single pass}
    \label{fig:magnet_design}
\end{figure}
From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
\begin{eqnarray}
    L_{in} &=& 2R_2 \nonumber\\
    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
\end{eqnarray}
After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
\begin{eqnarray}
    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
\end{eqnarray}
\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints. As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.

>>>>

\section{Magnet Design} \label{sec:magnet_design}
Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/Ltot.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/tt300_mag.png}
    \end{subfigure}
    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}}
    \label{fig:magnet_design_illustrations}
\end{figure}
In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
Time spent outside of the RF cavity should be precisely tuned to maximize acceleration in the succeeding pass.

@@

To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field. 
In other words, total trajectory of synchronous particle needs to satisfy the following equality:
\begin{equation}
    L_{pass} = n \lambda
\end{equation} 
Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice:
\begin{equation}
    L_{pass} = \lambda
\end{equation}

\begin{figure}[H]    
    \centering
    \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
    \caption{Trejectory of a particle in single pass}
    \label{fig:magnet_design}
\end{figure}
From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, 
$L$ is the length of the magnet guide, $d$ is the thickness of the RF cavity wall:
\begin{eqnarray}
    L_{in} &=& 2R_2 \nonumber\\
    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
\end{eqnarray}
After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
\begin{eqnarray}
    \tan (\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
    \rho &=&  \tan (\gamma) (R_2 + d + L) \nonumber\\
    2\rho &=& \tan (\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
    \rho (2 + \tan (\gamma)(\pi + 2\gamma)) &=&  \tan (\gamma) \lambda \nonumber\\
    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{\tan (\gamma)}} \label{eq:magnet_rho_constraint} \\
    L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 \label{eq:magnet_L_constraint}
\end{eqnarray}
\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints. As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.

### 2023-08-17 subsections/future/future_work.tex
changes from Erkcan & Gokhan hocas

\chapter{FUTURE WORK}

At the time of publication, production efforts of a new rhodotron type electron accelerator are currently continuing in KAHVELab. 
Present bottleneck is the fabrication of the cavity.

\section{Cavity}
The cavity manufacturing process is in its concluding stages.
The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
After the heat treatment operation, 
the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.

\section{Magnets}
Magnet production was decided to be kept on hold in the early stages of the project, 
due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
The software is planned to be used in magnet design and beam optimizations in KAHVELab after the initial tests are completed.

\section{Rhodotron Simulation}

\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manifactured; 
several improvements and new feature implementations are underway in the mean time. 
They include the following;
\begin{figure}[H]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Electric and magnetic field import
            \item Field generator module to directly produce field files from specified cavity
            \item Synchrotron radiation calculations to determine radiation and energy loss
            \item \ee interactions
            \item Redesign of the GUI
            \item 3D render in GUI
        \end{itemize}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Refactoring of the \eEM interaction and logging to improve performance
            \item Refactoring of the GUI Render Frame to improve render speed
            \item Refactoring the magnet class to introduce field leaks
            \item Extention of analysis tools in Analyze Frame
            \item $L_{out}$ sweep in Sweep Frame
        \end{itemize}
    \end{subfigure}
\end{figure}

\section{Conclusion}

In conclusion, the performance and the accuracy of this new tool, \textit{Rhodotron Simulation}, cannot be determined
before the cavity production is completed and the performance is compared with the predictions of the tool;
however the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
lead to the inference that this tool holds promise.
%%%%%%

>>>>

\chapter{CONCLUSION}
At the time of publication, production efforts of a new rhodotron type electron accelerator are currently continuing in KAHVELab. 
Present bottleneck is the fabrication of the cavity.

\section{Future Work}
Regarding the cavity manufacturing process, it is in the concluding stages.
The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
After the heat treatment operation, 
the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.

As far as the magnets concerned, it was decided to be kept on hold in the early stages of the project, 
due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
The software is planned to be used in magnet design and beam optimizations in KAHVELab after the initial tests are completed.

\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
several improvements and new feature implementations are underway in the mean time. 
They include the following;
\begin{figure}[H]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Electric and magnetic field import
            \item Field generator module to directly produce field files from specified cavity
            \item Synchrotron radiation calculations to determine radiation and energy loss
            \item \ee interactions
            \item Redesign of the GUI
            \item 3D render in GUI
        \end{itemize}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Refactoring of the \eEM interaction and logging to improve performance
            \item Refactoring of the GUI Render Frame to improve render speed
            \item Refactoring the magnet class to introduce field leaks
            \item Extention of analysis tools in Analyze Frame
            \item $L_{out}$ sweep in Sweep Frame
        \end{itemize}
    \end{subfigure}
\end{figure}
After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 
Complementary bending magnet design will be the first challange of \textit{Rhodotron Simulation}, which will provide tremendous testing and improvement opportunuties.

\section{Discussion}
In conclusion, a new computational \eEM interaction simulation and analysis tool that focuses on designing and improving \textit{Rhodotron-type} accelerators has been successfully developed; 
a \textit{Rhodotron-type} accelerator with an operating frequency of $107.5$ MHz and a target energy of $1-5$ MeV has been designed and is currently being manufactured.

The software features a robust GUI that is capable of rendering and analyzing simulation results.
Leap-frog and Runge-Kutta numerical methods have been implemented for initial speed and accuracy tests.
The real-world performance and accuracy of this new tool, on the other hand, cannot be tested
before the cavity production is completed and the performance is compared with the predictions of the tool;
however, the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
lead to the inference that it holds promise.
%%%%%%

### 2023-08-17 subsections/production/technical_drawings/techd.tex
başlık eklendi
changes from Erkcan & Gokhan hocas

%%%%%%
% Start of mani.tex
\section{Manifacturing}

%%%%%%

>>>>

%%%%%%
% Start of techd.tex
\section{Technical Drawing}
Technical drawings of the design mentioned in \fromsec{final_design} can be found in \fromfigs{techd_rhod}{techd_mid}, \fromfig{techd_up} of \fromapp{supp}.
\begin{figure}
    \centering
    \includegraphics[angle=270,origin=c, width=.98\linewidth]{../../../figures/teknikcizim/Rho-A1.0.00.pdf}
    \caption{Technical drawing of the rhodotron cavity. \cite{sinan}}
    \label{fig:techd_rhod}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[angle=270,origin=c, width=\linewidth]{../../../figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
    \caption{Technical drawing of middle part of the cavity which contains the beam line. \cite{sinan}}
    \label{fig:techd_mid}
\end{figure}
%%%%%%

### 2023-08-17 subsections/simulation/gui/gui.tex
changes from Erkcan & Gokhan hocas

\subsection{Simulation Frame}
This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
    \caption{Simulate frame of \textit{GUI}.}
    \label{fig:gui_simulate_1}
\end{figure}

\subsection{Render Frame}
Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
see a specific time frame, export as snapshot or animated gif file.
Two example renders can be seen in \fromfigs{gui_render_1}{gui_render_2}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
    \caption{Render frame of \textit{GUI}.}
    \label{fig:gui_render_1}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
    \caption{Render frame of \textit{GUI}.}
    \label{fig:gui_render_2}
\end{figure}

\subsection{Analyze Frame}
Analyze frame provides tools for analyzing and visualizing the simulation data. 
In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist.png}
    \caption{Analyze frame of \textit{GUI} E distribution.}
    \label{fig:gui_analyze_Edist}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_2.png}
    \caption{Analyze frame of \textit{GUI} E(t).}
    \label{fig:gui_analyze_Et2}
\end{figure}

\subsection{Sweep Frame}
Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
$\phi_{lag}$ sweep was the first parameter to be implemented. 
It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
This enables user with an already built accelerator to optimize \egun parameters quickly. 
In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_running.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
    \label{fig:gui_sweep_running}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
    \label{fig:gui_sweep_muE}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
    \label{fig:gui_sweep_sE}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sR.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
    \label{fig:gui_sweep_sR}
\end{figure}
As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
New analysis and sweep features will be implemented and current capabilities will be improved in the near future.

>>>>

\subsection{Simulation Frame}
This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.

\subsection{Render Frame}
Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
see a specific time frame, export as snapshot or animated gif file.
Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
    \caption{Render frame of \textit{GUI}.}
    \label{fig:gui_render_1}
\end{figure}

\subsection{Analyze Frame}
Analyze frame provides tools for analyzing and visualizing the simulation data. 
In the current version, \textbf{E} distribution histogram and \textbf{E(t)} graph of each electron are implementated into this frame.
This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist.png}
    \caption{Analyze frame of \textit{GUI} E distribution.}
    \label{fig:gui_analyze_Edist}
\end{figure}

@@

\subsection{Sweep Frame}
Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
$\phi_{lag}$ sweep was the first parameter to be implemented.

It takes the range of sweep, draws $\phi_{lag}$ vs $\mu E$, $\phi_{lag}$ vs $\sigma E$ and $\phi_{lag}$ vs $\sigma R$ mentioned in \fromsec{philag_sweep}.
This enables user with an already built accelerator to optimize \egun parameters quickly. 
In the \fromfigf{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_running}{gui_sweep_sR} of \fromapp{supp}, this frame can be inspected in detail.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
    \label{fig:gui_sweep_muE}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
    \label{fig:gui_sweep_sE}
\end{figure}

As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
